---
title: "Library of Optimized Breeding Schemes"
author: "Giovanny Covarrubias-Pazaran"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Library of Optimized Breeding Schemes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The lobs package is nice wrapper of the AlphaSimR package that enables to ask specific breeding scheme optimization questions.

The vignettes aim to provide several examples in how to use the lobs package under different optimization scenarios. We will spend the rest of the space providing examples for: 

1) Optimizing the number of environments and progeny tested per environment
2) ...

Because of CRAN requirements I will only run few generations but please when you run your analysis let it run for many generations.

### 1) Optimizing the number of environments and progeny tested per environment

```{r setup, include=FALSE} 
library(lobs)
```

```{r}
res <- sparset(gridEnvs = seq(5,15,5), gridInds = seq(10,300,30), 
               nCrosses=50, nProgeny=20, nIters = 10 )
plot.sparsetMod(res)
```

You can observe how using very few entries in few environments does not provide a good accuracy. At about 120 individuals the accuracy stabilizes and going beyond that doesn't seem to pay off.There seems to be a big room for improvement when the number of environments goes from 5 to 10.

## Literature

Giovanny Covarrubias-Pazaran (2025).  lobs: a library of optimized breeding schemes questions. To be submitted to Bioinformatics.

Gaynor, R. Chris, Gregor Gorjanc, and John M. Hickey. 2021. AlphaSimR: an R package for breeding program simulations. G3 Gene|Genomes|Genetics 11(2):jkaa017. https://doi.org/10.1093/g3journal/jkaa017.

Chen GK, Marjoram P, Wall JD (2009). Fast and Flexible Simulation of DNA Sequence Data. Genome Research, 19, 136-142.
